\pkg{fitdistrplus}: An \proglang{R} Package for Distribution Fitting Methods

### 2013-03-28 JSS/fitdistrplus/paper2JSS.Rnw
new version of the paper for an easier compilation and with my affiliation modified
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/riskassessment@237 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\author{ Marie Laure Delignette-Muller \\ Université Claude Bernard Lyon 1 \And
    Christophe Dutang \\ Université de Strasbourg}
\Plainauthor{Marie Laure Delignette-Muller}

@@

\Address{
    Marie Laure Delignette-Muller \\
    VetAgro Sup Campus Vétérinaire de Lyon \\
    1, avenue Bourgelat \\
    69820 MARCY L'ETOILE\\
    France \\
    E-mail: \email{marielaure.delignettemuller@vetagro-sup.fr} \\
    URL: \url{http://lbbe.univ-lyon1.fr/-Delignette-Muller-Marie-Laure-.html}
}

@@

%\bibliographystyle{plain}
\bibliography{../vignettes/fitdistrplus,../vignettes/paperscitingfitdistrplus}

>>>>

\author{ Marie Laure Delignette-Muller \\ Universit\'e de Lyon \And
    Christophe Dutang \\ Universit\'e de Strasbourg}
\Plainauthor{Marie Laure Delignette-Muller}

@@

\Address{
    Marie Laure Delignette-Muller \\
    Universit\'e de Lyon\\
    Universit\'e Lyon 1, CNRS, UMR5558, Laboratoire de Biom\'etrie et Biologie \'evolutive\\
    VetAgro Sup, Campus V\'et\'erinaire de Lyon \\
    1, avenue Bourgelat \\
    69820 MARCY L'ETOILE\\
    France \\
    E-mail: \email{marielaure.delignettemuller@vetagro-sup.fr} \\
    URL: \url{http://lbbe.univ-lyon1.fr/-Delignette-Muller-Marie-Laure-.html}
}

@@

%\bibliographystyle{plain}
\bibliography{fitdistrplus,paperscitingfitdistrplus}
